High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
all run
60000

```{julia}
# Model parameters:
epochs = 10
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```

```{julia}
# JEM parameters:
𝒟x = Uniform(-1.0,1.0)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=10,
)
α = [1.0,1.0,1e-2]      # penalty strengths
```

@@

# Final model:
lenet = NeuralNetworkClassifier(
    builder=LeNetBuilder(5, 6, 16),
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)
```

@@

```{julia}
combos = [
    (7,2),
    (0,8),
    (8,3),
    (9,4),
]

plts = [plt_additional_models]

>>>>

```{julia}
# Model parameters:
epochs = 25
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```

```{julia}
# JEM parameters:
𝒟x = Uniform(-1.0,1.0)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=10,
)
α = [1.0,1.0,25e-3]      # penalty strengths
```

@@

# Final model:
lenet = NeuralNetworkClassifier(
    builder=LeNetBuilder(5, 6, 16),
    epochs=50,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)
```

@@

```{julia}
combos = [
    (7,2),
    (0,8),
    (8,3),
    (9,7),
    (4,9),
    (2,1),
    (3,5),
    (5,8),
    (6,0),
    (1,7),
]

plts = []
